Sperm should evolve to make female meiosis fair.

### 2015-01-18 writeup_and_notes/evolution/RESUBMISSIONmale_dependent_drive.tex
added to acknowledgements

%%!TEX TS-program = latex
\documentclass[12pt,letterpaper]{article}
\bibliographystyle{evolution}
\usepackage{epsfig}                 
\usepackage[authoryear]{natbib}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{psfrag}
\usepackage{mathabx}
\renewcommand{\baselinestretch}{1.6}
\large
\pagenumbering{arabic}
\usepackage[usenames,dvipsnames]{color}
\usepackage{fullpage}
\usepackage{multirow}
\newcommand{\ye}{\hat{y}}
\newcommand{\xe}{\hat{x}}
\usepackage{color}
\usepackage[normalem]{ulem}  
	\newcommand{\gc}[1]{{ \color{red} #1}}
	\newcommand{\yb}[1]{{ \color{blue} #1}}
\usepackage{lineno}
\linenumbers

@@

\newpage 
\section*{Acknowledgements}
We would like to thank members of the Coop lab for comments. This work was made possible by the NSF Postdoctoral Fellowship in Biology FY 2010 project number 1002942 awarded to Y.B..
\newpage 
\bibliography{refs}
\newpage 
  \appendix

@@

\begin{figure}
%\includegraphics[width = \textwidth]{supp/meiotic_phylogeny.pdf}
\caption{The phylogenetic distribution of the female meiotic
  arrest. The first two columns of symbols gives the stage of the ooycte when
  the sperm penetrates and the stage at which it arrests if
  unfertilized. The third column of symbols shows the site for natural fertilization. 
  These columns of phenotypic data were extracted from Table
  1 of \citet{Masui_book}. The tree was extracted from the Open Tree of
Life project. The raw data table, the phylogeny/supporting R objects, and the script to do this is are included in
the supplement (Files S4-S6). }  
\label{Meiotic_fig}
\end{figure}

>>>>

%%!TEX TS-program = latex
\documentclass[12pt,letterpaper]{article}
\bibliographystyle{evolution}
\usepackage{epsfig}                 
\usepackage[authoryear]{natbib}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{psfrag}
\usepackage{hyperref}
\usepackage{mathabx}
\renewcommand{\baselinestretch}{1.6}
\large
\pagenumbering{arabic}
\usepackage[usenames,dvipsnames]{color}
\usepackage{fullpage}
\usepackage{multirow}
\newcommand{\ye}{\hat{y}}
\newcommand{\xe}{\hat{x}}
\usepackage{color}
\usepackage[normalem]{ulem}  
	\newcommand{\gc}[1]{{ \color{red} #1}}
	\newcommand{\yb}[1]{{ \color{blue} #1}}
\usepackage{lineno}
\linenumbers

@@

\newpage 
\section*{Acknowledgements}
We would like to thank members of the Coop lab for comments, and Jon
Wilkins, Andrew Gardner, and an anonymous reviewer for helpful
comments on an earlier version of the paper. This work
was made possible by the NSF Postdoctoral Fellowship in Biology FY
2010 project number 1002942 awarded to Y.B. and by grants from the
National Science Foundation under Grant No. 1262645 and by the
National Institute of General Medical Sciences of the National
Institutes of Health under award numbers NIH RO1GM83098 and
RO1GM107374 to GC. We thank Karen Cranston, Fran\c{c}ois Michonneau,
and David Winter for assistance with the R open tree of life package
used to produce Figure \ref{Meiotic_fig}. % ç

\newpage 
\bibliography{refs}
\newpage 
  \appendix

@@

\begin{figure}
%\includegraphics[width = \textwidth]{supp/meiotic_phylogeny.pdf}
\caption{The phylogenetic distribution of the female meiotic
  arrest. The first two columns of symbols gives the stage of the ooycte when
  the sperm penetrates and the stage at which it arrests if
  unfertilized. The third column of symbols shows the site for natural fertilization. 
  These columns of phenotypic data were extracted from Table
  1 of \citet{Masui_book}. The tree was extracted from the Open Tree of
Life project (\url{https://github.com/fmichonneau/rotl}). The raw data table, the phylogeny/supporting R objects, and the script to do this is are included in
the supplement (Files S4-S6). }  
\label{Meiotic_fig}
\end{figure}
